The algorithm itself is more sketched than described and I would rather see a little bit more detailed description.

Authors should proof-read their abstract in order avoid language errors 

simplistic assumptions

The paper doesn't state the underlying assumptions of the learning approach and doesn't present explicitly the data model. Moreover, the paper doesn't state the number of mobility classes.

The paper should improve its methodologic approach. For example, while the prediction task is (also) about classification ("... associates to each class of mobility...") authors consider accuracy as the only performance metric. 

Furthermore, authors should justify better the choice of LSTM network when according to their statement the nodes have small/poor datasets.


- The LSTM parameters could be presented for a better understanding of the model and allow replications.
- The authors can indicate the main parameters used in the construction of the LSTM model.
- The three proposed algorithms' differences can be presented in a single image, with the appropriate indications.
- Authors can indicate which applications would benefit from this distributed learning, reinforcing the importance of proposing algorithms in this context.

DONE

- What is an MNO? The authors do not define in the text.
- The approaches have good results when the vehicles remain in the scenario for about 20 minutes. Perhaps an assessment of which applications have acceptable requirements for decision-making over 20 minutes is interesting.